\Annex{informative}{Implementation Documentation}{AnnexB}

\Sec{Pre-standard Language Versions}{AnnexB.Versions}

\p HLSL has evolved over time, with various versions of the language being
released alongside different versions of DirectX. Beginning with the DirectX
Shader Compiler (DXC), the compiler began supporting language modes
corresponding to specific historical versions of HLSL. These historical versions
are useful for understanding the evolution of the language and for documenting
observed behaviors in specific implementations, and they are named for the years
in which they were released. The following historical versions of HLSL are
relevant to this specification:

\begin{itemize}
  \item \textbf{HLSL 2015}: Roughly equivalent to the version of HLSL supported
  by the Effects Compiler (FXC).
  \item \textbf{HLSL 2016}: The initial version of HLSL supported by the DirectX
  Shader Compiler (DXC).
  \item \textbf{HLSL 2017}: Added enumerations similar to C++11.
  \item \textbf{HLSL 2018}: Added support for 16-bit data types and intrinsic
  templates.
  \item \textbf{HLSL 2021}: Added user-defined templates, operator overloading,
  short-circuiting boolean operators, and stricter implicit casting rules for
  user-defined structures.
\end{itemize}

\begin{note}
Both the DirectX Shader Compiler (DXC) and Clang support a language mode called
"HLSL 202x" which refers to this draft specification.
\end{note}

\Sec{Known Implementations}{AnnexB.Implementations}

\p This section provides a list of known implementations of HLSL, including both
conforming and non-conforming implementations. This is not meant to be
comprehensive, but is provided to supplement later sections in this annex which
discuss details of specific implementations.

\begin{itemize}
  \item \textbf{Clang}: The open-source C/C++ compiler developed by the LLVM
    project. Clang contains a partial implementation of HLSL this specification
    and is actively being developed. It is available at
    \url{https://clang.llvm.org/}.
  \item \textbf{DirectX Shader Compiler (DXC)}: The open-source reference
    implementation of HLSL, developed by Microsoft and based on the LLVM/Clang
    infrastructure. It is available at
    \url{https://github.com/microsoft/DirectXShaderCompiler}.
  \item \textbf{Effects Compiler (FXC)}: The legacy implementation of HLSL,
    developed by Microsoft. It is included with the Windows SDK and is available
    at \url{https://learn.microsoft.com/en-us/windows/apps/windows-sdk/}.
  \item \textbf{GLSLang}: An open-source implementation of the OpenGL Shading
    Language (GLSL), developed by The Khronos Group. GLSLang contains a (now
    deprecated) partial implementation of HLSL 2018. It is available at
    \url{https://github.com/KhronosGroup/glslang}.
  \item \textbf{Slang}: An open-source shader language and compiler framework
    developed by The Khronos Group. Slang contains a partial implementation of
    HLSL 2018. It is available at \url{https://github.com/shader-slang/slang}.
\end{itemize}

\Sec{Implementation Limits}{AnnexB.Limits}

\p This section describes reasonable implementation limits that may be assumed
by a conforming implementation. These limits specify minimum required or maximum
allowed values for various implementation-defined parameters.

\p \ref{Basic.Types} declares a vector type as having required supported sizes
of 1 to 4 components. Implementations may support larger vector sizes but are
not required to do so. An implementation that supports larger vector sizes must
define its vector size limit.

\Sec{Observed Deviations}{AnnexB.Documentation}

\p This section provides documentation around implementation behaviors that are
known to differ between specific implementations. This includes breaking
changes between historical HLSL and standard HLSL where some compilers or
versions of compilers may not conform to standard HLSL, as well as observed
non-conformant behaviors in such compilers. This is not meant to be a
comprehensive list of bugs.

\Sub{Resource Objects}{AnnexB.Resources}

\p In violation of \ref{Basic.Types.Intangible}, DXC supports storing objects
that contain resources in \texttt{cbuffer} declarations. In this use case the
resource objects are not actually stored in the \texttt{cbuffer}, but instead
the resource is treated as a global resource declaration and name lookup
resolves the value inside the structure declaration to the implied global
resource declaration.
