\Ch{Library Overview}{Library}

\p This clause serves as an overview to the remaining clauses of the
specification which detail \acrshort{hlsl}'s standard library of functions and
objects.

\Sec{Syntax Notations}{Library.Notation}

\p Some of the constructs in the standard library are not expressible with
spellable syntax. This section describes syntax constructs which are
non-standard but are used throughout the standard library specification.

\p Code blocks in the remaining clauses of the specification decribe a
hypothetical implementation and are provided for clarity. A conforming
implementation need not rely on the specifc code in any of the blocks.

\Sub{Constructors}{Library.Notation.Constructors}

\p Some standard library types have behaviors associated in \gls{isoCPP} with
constructors. These syntaxes are intended to describe equivalent behavior with
C++ constructors.

\Sub{Reference Types}{Library.Notation.References}

\p Some standard library functions or member functions behave as if a parameter
or return value are references (passed by address or returned by address). To
simplify this notation the syntax \textit{address-space\textsubscript{opt}}
\texttt{T \&} is used where the optional \textit{address-space} is one of
\texttt{device} or \texttt{groupshared}.

\Sub{Concepts}{Library.Notation.Concepts}

\p Some standard library template functions or objects have constraints to which
types are valid as template arguments. To simplify this notation the concepts
syntax from \gls{isoCPP20} is used.

\Sec{Method of Description (Informative)}{Library.Method}

\Sub{Clause Structure}{Libarry.Method.Structure}

\p Each library clause will contain all applicable subclauses of the list:

\begin{itemize}
  \item Introduction
  \item Optional features
  \item Special semantics
  \item Element subclauses
\end{itemize}

\p The clause introduction shall provide an overview of the contents of the
clause. Some features detailed in a clause may be optional, a subclause
describing the optional features will be included if applicable.

\p Each library clause will optionally contain a subclause describing additional
semantic behaviors required for the clause. This subclause is omitted if empty.

\p Each library clause will contain one or more element subclauses detailing the
declarations required in a conforming implementation of the specification, and
any normative optional declarations based on optional features described in the
clause.

\SubSub{Element Subclauses}{Library.Method.Structure.Element}

\p Each element subclause contain the following:

\begin{itemize}
  \item Summary
  \item Detailed specifications
\end{itemize}

\SubSub{Summary}{Library.Method.Structure.Summary}

\p The summary will include a description of the category as well as a listing
of any introduced headers, macros, and declarations.

\SubSub{Detailed Specification}{Library.Method.Structure.Detailed}

\p The detailed specification for each entity will contain each of the below
that apply:

\begin{itemize}
  \item name and description
  \item class definition or function prototype
  \item template argument constraints
  \item class invariants
  \item function semantics
\end{itemize}

\p Description of class member functions will follow the order, omitting
sections that are empty:

\begin{itemize}
  \item Constructors
  \item Copying and assignment
  \item Modifying functions
  \item Inspection functions
  \item Operators
  \item Other non-member functions
\end{itemize}

\p Descriptions of function semantics will contain all of the following elements
that apply in the order as specified:

\begin{itemize}
  \item \textit{Requires:} the preconditions for calling the function.
  \item \textit{Effects:} the actions performed by the function.
  \item \textit{Synchronization:} the requirements for execution or memory
  synchronization.
  \item \textit{Returns:} a description of the value returned by the function.
  \item \textit{Remarks:} additional normative information about the function.
  \item \textit{Notes:} non-normative information provided about the function.
\end{itemize}
